Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-24 SDSS-2023/testing-charts-accuracy.qmd
just a comment

The resulting model estimates and confidence intervals are displayed in \autoref{tbl-zoom-123}. We can observe that zooming behavior *only* differs significantly by structural design; rates do not differ significantly between the aligned and unaligned tasks, nor do they differ significantly by the chosen response. This higher rate of zooming does not necessarily lead to higher accuracy; although rates of accuracy are significantly higher for the vertical orientation relative to the horizontal orientation, they are not significantly higher -- and in fact, are significantly lower on the aligned task -- than the accuracy for the horizontal wide orientation.  \hh{I'll pretty up @tbl-zoom-123 if we are going to keep it.} \kr{I think we should! it's nice to have a model for this}

>>>>

The resulting model estimates and confidence intervals are displayed in \autoref{tbl-zoom-123}. We observe that zooming behavior *only* differs significantly by structural design; rates do not differ significantly between the aligned and unaligned tasks, nor do they differ significantly by the chosen response. This higher rate of zooming does not necessarily lead to higher accuracy; although rates of accuracy are significantly higher for the vertical orientation relative to the horizontal orientation, they are not significantly higher -- and in fact, are significantly lower on the aligned task -- than the accuracy for the horizontal wide orientation.  \hh{I'll pretty up @tbl-zoom-123 if we are going to keep it.} \kr{I think we should! it's nice to have a model for this}\hh{gt and rmarkdown are frustrating! I'll re-set the table in its final form directly in tex}
